Create additional figures

### 2020-10-30 R/create_figures.Rmd
workflow figure?
trying to make one using DiagrammeR but can't figure out how to export it as pdf

>>>>

## Workflow figure

```{r}
library(DiagrammeR)
library(rsvg)

workflow <- DiagrammeR::grViz("digraph {

graph [layout = dot, rankdir = LR]

# define the global styles of the nodes. We can override these in box if we wish
node [shape = rectangle, style = filled, fillcolor = Linen]

data1 [label = 'In-situ plant \nmeasurements', shape = folder, fillcolor = LightSteelBlue3]
data2 [label = 'Hyperspectral \nreflectance', shape = folder, fillcolor = LightSteelBlue3]
process1 [label =  'Extract \n Reflectance', fillcolor = Gainsboro]
process2 [label = 'Data cleaning & \nPreparation', fillcolor = Gainsboro]
classify1 [label = 'Classify Species', fillcolor = AntiqueWhite3]
classify2[label = 'Classify Genus', fillcolor = AntiqueWhite3]
results [label= 'Results', shape = oval, fillcolor = Honeydew3]

# edge definitions with the node IDs
{data1 data2}  -> process1 -> process2 -> {classify1 classify2} -> results
}")

workflow

export_graph(workflow,
  file_name = here::here("analysis", "figures", "workflow.pdf"),
  file_type = "pdf")

DiagrammeR::export_graph(workflow) %>%
  charToRaw() %>%
  rsvg::rsvg_pdf(here::here("analysis", "figures", "workflow.pdf"))

#grViz(workflow) %>%
#    export_svg %>% charToRaw %>% rsvg_pdf(here::here("analysis", "figures", "workflow.pdf"))
```
